### 2020-02-05 ncov.tex
one more comment!

>>>>

\swp{Some of the papers that we look at have been published now. Where do we want to address that? Discussion? Methods? I'm thinking of adding a sentence to the Methods section where we review 7 papers: ``Some of these studies have now been published in peer reviewed journals or have been updated with better quantification of uncertainties [CITE].'' I think this is a fair thing to say.}
